### 2017-04-06 sections/implementation.tex
Update on Overleaf.

\begin{equation}
\mtrx{A}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{n}}S_{n}\mtrx{V_{n}^{T}},
\label{eq:svd-expansion}
\end{equation}

@@

\begin{equation}
\mtrx{A'}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{r}}S_{r}\mtrx{V_{r}^{T}}.
\label{eq:svd-approx-expansion}
\end{equation}

@@

The main goal of the compression algorithm is to find a compromise between low approximation error and high compression ratio $CR$ which is calculated using the formula

\begin{equation}
CR=\frac{r(m+n+1)}{m n},
\label{eq:cr-def}
\end{equation}

@@

\begin{figure}[H]
\centering\includegraphics[width=0.7\textwidth]{figures/low_rank_decomposition_diagram}
\caption{Decomposition of input matrix $\mtrx{A}$ into diagonal matrix of singular values $\mtrx{\Sigma}$ and matrices of left and right singular vectors. Light color illustrates low-rank approximation.}
\label{fig:lowrank_svd}
\end{figure}

@@

\begin{equation}
r=\ceil*{CR \times \frac{m n}{m+n+1}},
\end{equation}

\noindent
where $CR$ is the compression ratio, $0 \leq CR \leq 1$ ($0$ results in absolute compression while $1$ results in no compression).

>>>>

%\begin{equation}
%\mtrx{A}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{n}}S_{n}\mtrx{V_{n}^{T}},
%\label{eq:svd-expansion}
%\end{equation}

\begin{equation}
\mtrx{A}=\sum_{i=1}^{n} \mtrx{U_{i}}S_{i}\mtrx{V_{i}^{\mathsf{T}}},
\label{eq:svd-expansion}
\end{equation}

@@

%\begin{equation}
%\mtrx{A'}=\mtrx{U_{1}}S_{1}\mtrx{V_{1}^{T}}+\mtrx{U_{2}}S_{2}\mtrx{V_{2}^{T}}+ ... +\mtrx{U_{r}}S_{r}\mtrx{V_{r}^{T}}.
%\label{eq:svd-approx-expansion}
%\end{equation}

\begin{equation}
\mtrx{A'}=\sum_{i=1}^{r} \mtrx{U_{i}}S_{i}\mtrx{V_{i}^{\mathsf{T}}}.
\label{eq:svd-approx-expansion}
\end{equation}

@@

The main goal of the compression algorithm is to find a compromise between low approximation error and high compression ratio $c$ which is calculated using the formula

\begin{equation}
c=\frac{r(m+n+1)}{m n},
\label{eq:cr-def}
\end{equation}

@@

\begin{figure}[H]
\centering\includegraphics[width=0.7\textwidth]{figures/low_rank_decomposition_diagram}
\caption{Decomposition of input matrix $\mtrx{A}$ into diagonal matrix of singular values $\mtrx{S}$ and matrices of left and right singular vectors. Light color illustrates low-rank approximation.}
\label{fig:lowrank_svd}
\end{figure}

@@

\begin{equation}
r=\ceil*{c \times \frac{m n}{m+n+1}},
\end{equation}

\noindent
where $c$ is the compression ratio, $0 \leq c \leq 1$ ($0$ results in absolute compression while $1$ results in no compression); $\ceil*{.}$ is the ceiling function.
